Predicting the PCG PSeudo-Random Number Generator In Practice

### 2020-05-28 article/main.tex

In this article, we will only use the Babai's rounding when \(k = 128-\ell\) and when we know the \(6\) upper bit of our Lehmer's generator. Hence \(\lVert T-U \rVert \leqslant \sqrt{n}2^{122-\ell} \). So, if we fix \(\ell\) we can search for the minimum \(n\) such that \[2\sqrt{n}2^{122-\ell} \leqslant \lambda_1(L(128-\ell,n))\].

\begin{table}
  \centering
    \begin{tabular}{|c|c|}
	\hline
	\(\ell\)  & minimum \(n\) \\
	\hline
	11 & 39 \\
	12 & 38 \\
	13 & 38 \\
	\hline
\end{tabular}
  \caption{\todo{WRITE-ME}}
  \label{tab:exact_cvp}
\end{table}

@@

\bigskip

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|}
	\hline
	n & \(\lVert G(n,64) \rVert \times \lVert G(n,64)^{-1} \rVert\) & \( \lambda_1(L(n,64)) \) & minimum \(\ell\) \\
	\hline
	3 & 2.869065991049632 & \(4.08909120094543e^{12}\) & 19 \\
	4 & 2.060717188416003 & \(2.43569932844650e^{14}\) & 13 \\
	5 & 3.7692142154392747 & \(1.71669732658884e^{15}\) & 11 \\
	6 & 2.6925925483728537 & \(1.02550589786192e^{16}\) & 8 \\
	\hline
  \end{tabular}
  \caption{\todo{WRITE-ME}}
  \label{tab:babai}
\end{table}

>>>>

To compute \(\lambda_1(L)\), we find the shortest vector of L thanks to an exact SVP solver (SVP stands for Shortest Vector Problem) and we compute its norm.

In this article, we will only use an exact CVP solver when \(k = 128-\ell\) and when we know the \(6\) upper bit of our Lehmer's generator. Hence \(\lVert T-U \rVert \leqslant \sqrt{n}2^{122-\ell} \). So, if we fix \(\ell\) we can search for the minimum \(n\) such that \[2\sqrt{n}2^{122-\ell} \leqslant \lambda_1(L(128-\ell,n))\].

\begin{table}[htbp!]
  \centering
    \begin{tabular}{|c|c|}
	\hline
	\(\ell\)  & minimum \(n\) \\
	\hline
	0  & 42 \\
	11 & 39 \\
	12 & 38 \\
	13 & 38 \\
	\hline
\end{tabular}
  \caption{\todo{WRITE-ME}}
  \label{tab:exact_cvp}
\end{table}

@@

\begin{table}[htbp!]
  \centering
  \begin{tabular}{|c|c|c|c|}
	\hline
	n & \(\lVert G(n,64) \rVert \times \lVert G(n,64)^{-1} \rVert\) & \( \lambda_1(L(n,64)) \) & minimum \(\ell\) \\
	\hline
	3 & 2.869065991049632 & \(4.08909120094543e^{12} \simeq 2^{42}\) & 19 \\
	4 & 2.060717188416003 & \(2.43569932844650e^{14} \simeq 2^{48}\) & 13 \\
	5 & 3.7692142154392747 & \(1.71669732658884e^{15}\simeq 2^{51}\) & 11 \\
	6 & 2.6925925483728537 & \(1.02550589786192e^{16}\simeq 2^{53}\) & 8 \\
	\hline
  \end{tabular}
  \caption{\todo{WRITE-ME}}
  \label{tab:babai}
\end{table}
